{Contextual Learning with Integrated Least Effort Knowledge Networks}

### 2016-10-24 proposal.tex
touching up proposal

We present the SKN framework ({\bf S}cale-free {\bf K}nowledge {\bf
N}etwork), capable of contextualizing knowledge in an abstract manner.
Knowledge can be represented as distinct atoms of information and their
relations in the structure of a connected network. The network is
constructed by preferential ``least effort'' attachment
\cite{barabasi99}\cite{cancho03}, where the learning of a new atom of
knowledge joins the network with relations to the contextual knowledge from
which it was learned based on memory access. This network is scale-free ---
it conforms to a mathematical pattern similar to that of Zipf's Law
\cite{zipf49}, where the degree of connectivity for nodes in the network
follow a class of power law distributions.

@@

To experiment with SKN, consider the class of problems for which this system
would excel: complex domains where modular knowledge improves the efficiency
of completing relevant tasks. We augment a system for learning via iterative
modular concept discovery --- the EC algorithm \cite{dechter13} --- to
interface with SKN rather than use the traditional flat set of knowledge
items. The EC algorithm performs search on a stochastic grammar that is
expressive in a particular problem domain, and modifies the grammar's
generative distribution to include learned modular concepts which are useful
in representing tasks. The augmentation to utilize SKN will treat the
generative distribution as a mixture model that uses concepts which are
stored in the context. The augmented EC algorithm will be tested in the
domains of letter analogies \cite{hofstadter94}, L-systems
\cite{rozenberg80}, and Boolean circuits illustrated in Figure
\ref{fig:exps}, and compared to the original EC algorithm as well as a
baseline of search without knowledge assistance. These problem domains were
chosen because they each have potential for common underlying structure
between tasks. Results will be compared on the number of tasks solved given
number of iterations for the algorithm.

>>>>

To contextualize knowledge in an abstract manner, we develop the SKN
framework ({\bf S}cale-free {\bf K}nowledge {\bf N}etwork). Knowledge is
represented as distinct atoms of information and their relations in the
structure of a connected network. The network is constructed by preferential
``least effort'' attachment \cite{barabasi99}\cite{cancho03}, where the
learning of a new atom of knowledge joins the network with relations to the
contextual knowledge from which it was learned. This network is scale-free
--- it conforms to a mathematical pattern similar to that of Zipf's Law
\cite{zipf49}, where the degree of connectivity for nodes in the network
follow a class of power law distributions.

@@

To experiment with SKN, consider the class of problems for which this system
would excel: complex domains where modular knowledge improves the efficiency
of completing relevant tasks. There are many learning mechanisms which are
suitable for experimentation, such as inductive logic programming (ILP)
systems or algorithms which perform search on a grammar. Distinct items of
knowledge for ILP systems could be sets of predicates, and for grammar
search systems they could be language artifacts which construct a mixture
model on which search is performed.

\newpage
We augment an algorithm which performs search on a learned expressive
grammar, the EC algorithm \cite{dechter13}. The augmentation will define the
grammar based on learned language artifacts stored in the context, rather
than artifacts stored in a small bounded set. The modified EC algorithm will
be tested in the domains of letter analogies \cite{hofstadter94}, L-systems
\cite{rozenberg80}, and Boolean circuits illustrated in Figure
\ref{fig:exps}. These problem domains were chosen because they each have
potential for common underlying structure between tasks. Results will be
compared to the original EC algorithm on number of tasks solved given number
of iterations for the algorithm.
